An efficient contact value approach to approximating the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-07-15 papers/pair-correlation/paper.tex
Jeff's edit seems fine Tested on bennet. Took 0:20.01.

\jeffsays{I've edited the following paragraph but it should be
  checked.}  In this paper, we introduce a new contact value approach
(CVA) to approximating the hard-sphere pair distribution function
which is suitable for use in the creation of classical density
functionals based on thermodynamic perturbation theory. The resulting
function is based on a fit to the radial distribution function that is
separable in a way that will enable efficient evaluation of the
integral in Eq.~\ref{eq:mean-field}.

>>>>

In this paper, we introduce a new contact value approach
(CVA) to approximating the hard-sphere pair distribution function
which is suitable for use in the creation of classical density
functionals based on thermodynamic perturbation theory. The resulting
function is based on a fit to the radial distribution function that is
separable in a way that will enable efficient evaluation of the
integral in Eq.~\ref{eq:mean-field}.
